\documentclass[12pt,A5]{report}
%% We use book for printing, this adds extra pages so that things like chapters always start on the left side etc.
%% report is much like book, but not with extra pages 
% letter (8.5x11) and A4 (8.4x 11.7) are close but not quite.
% While A5 seems to be a good journal size
% You fav moleskine is "large" 5x8.25
\usepackage[utf8]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[shortlabels]{enumitem}
\usepackage{multicol}
\setlength{\columnsep}{1cm}

%% To change Chapter/Sections
\usepackage[T1]{fontenc}
\usepackage{titlesec}

%% Using Titlesec allows us to modify the chapters and sections to allow for stylazation without needing to modify the class
\titleformat
{\chapter} % command
[display] % shape
{\bfseries\Large\itshape} % format
{Chapter \ \thechapter} % label
{0.5ex} % sep
{
    \rule{\textwidth}{1pt}
    \vspace{1ex}
    \centering
} % before-code
[
\vspace{-0.5ex}%
\rule{\textwidth}{0.3pt}
] % after-code


\author{Andrew Brady}
\title{Hello Typeseting!}
\begin{document}
\pagenumbering{roman}
\maketitle
\tableofcontents


\chapter{Hello World!}
\pagenumbering{arabic}

\section{Introduction}
Hello World!!! That is generally how you get started in programming. While understanding how to make the typeset documents of our dreams. We will need to tackel a few things past that in this first chapter. \newline But what about a code listing?

\begin{verbatim}
10 PRINT "HELLO WORLD!"
20 GOTO 10
\end{verbatim}

That was a simple \verb|BASIC| program, did you like it? With a simple code listing out of the way I do think we can get started. Keep in mind that there is no syntax highlighting there, but it will be covered in future sections.

\section{What to cover?}
Moving allong with things, lets consider what we need to be able to cover. 

Now with a list of things we need to make sure we exersize.

\begin{multicols*}{3}

\begin{enumerate}
\item Code Listing
\item Quotes
\item Callout Boxes
\item Margin Notes
\item Diagrams
\item Columns
\item Rotated pages?
\end{enumerate}
\end{multicols*}

\section{Quote Example}
That is one of my favorate quotes from evloutionary biology. But I first saw it in \textit{The Psychology of Computer Programming}

\begin{quote}
"With Specialization, to a specifc enviroment a system will lose its ablity to adapt" - Gerald Weinberg

\end{quote}


\chapter{Moving Along...}

What happens if we put a little something here kinda like a summary at the beginning of a chapter

\section{Frist Princaples}

Let's discuss what "Frist Princaples" really means.

\end{document}