\section{Contact us}

Please address comments and questions concerning this book to the publisher \& community:
\begin{verbatim}
	Danger Brady Enterprises
	611 North Pine Street
	Rolla MO, 64501
\end{verbatim}

To comment or ask technical questions about this book, send email to:
	\textbf{FertileFramework@hackerhomestead.com}

\section{Resources}

I do really want this book to be able to stand on its own however here are some supporting resources to aid.
There is a web page for this book that lists errata, examples, and any additional information. You can access this page at:\\

	\textbf{https://www.hackerhomestead.com/FertileFramework}\\

To Engage with the community at large access our chat server via Discord:\\

	\textbf{	https://discord.gg/nxjvqgFQgJ}\\

For more information about books, projects, resources, and the Hacker Homestead, see:\\

	\textbf{	https://www.hackerhomestead.com}\\


There is a Hacker Homestead Youtube Channel where you may access videos related to this book and other projects at:\\

	\textbf{https://www.youtube.com/HackerHomestead}\\

Physical Materials such as computers, flash drives, and others mentioned in this book may be purchased on our Ebay Store\\

	\textbf{https://www.ebay.com/usr/hackerhomestead}\\

If you are a teacher looking to use this book in your classroom there are additional resources available, as well as support for purchasing a classroom set of computers compatible with the material.

\section{Acknowledgements}

Thanks for those who have helped put this together

\section{Companion Materials}

This book is intended to be a vertical slice of modern computing. While we may not cover everything you need to become a master, we will include attempt to include all software referenced along with critical documentation to explore more on your own. Another reason todo this is for historical and archival reasons.  The internet is a vast source of information, but it is also in constant flux links break, companies change hands, people simplicity investing in keeping things where they are. This is generally not an issue thanks for organizations and educational institutions such as the Internet Archive, Massachusetts Institute of Technology, University of California Berkeley and many more. If you are in the future and attempting to locate materials in this book and not having luck reach out to these folks as they likely have a copy. That being said preserving history is really up to all of us. So included with the book are flash or DVD materials with the essentials, and of course also on \textbf{https://www.hackerhomestead/}.
In the appendix you may find a proper index but this is a high level of what is included

    • Alpine  3.18.5 Linux Extended Live Image

    • Ubuntu 20.04 LTS Desktop Live image

    • Linux From Scratch Source Files (LFS)

        ◦ While you will need a bootdisk and some dependency's installed, nice thing is that LFS by default is built from the ground up and dose not rely on a package repo to put together. 

    • Beyond Linux From Scratch Source Files (BLFS)

        ◦ Same as LFS but more ;) 

    • Buildroot 2023

        ◦ Buildroot relies on downloading dependencies directly such as kernel source. We will attempt to include major releases of these dependency's and a means to reference them.

    • Documentation

        ◦ Intel resources and Datasheets – this is a valueable set of resources the provide a low level understanding of the x86 architecture, Including assembly language specifics

        ◦ BIOS Standards Documentation – For many ages BIOS was king

        ◦ UEFI Standards Documentation – This should include what you might need to understand more about how the UEFI framework works
